Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.tex
?

However, as children are learning from others around them, their view of
the world is also radically changing (K. Adolph \& Berger, 2007).
Infants' motor abilities improve dramatically near the end of the first
year of life, allowing them to locomote independently. These motor
changes have drastic consequences for what children see; crawling and
walking infants have radically different views of the world. For
example, during spontaneous play in a laboratory playroom, toddlers are
more likely to look at the floor while crawling than while walking (J.
Franchak, Kretch, Soska, \& Adolph, 2011); in general, walking infants
tend to have full visual access to their environment and the people in
it, while crawling infants do not (K. S. Kretch, Franchak, \& Adolph,
2014).

@@

Here, we directly ask whether postural and locomotive developments
change the availability of social information--the presence of faces and
hands. To do so, we recorded the visual experience of a group of infants
in three age ranges (8,12, and 16 months) using head-mounted cameras
during a brief laboratory free-play session; children's posture and
orientation relative to their caregiver were also recorded from a
third-person perspective and hand-annotated. We then capitalize on
recent improvements in face and pose detection algorithms (Cao, Simon,
Wei, \& Sheikh, 2017; K. Zhang, Zhang, Li, \& Qiao, 2016) to analyze the
frequencies of faces and hands (using wrist presence as a proxy for the
latter) in the child's visual environment, both overall and relative to
naming events by their caregivers. We hypothesized that there would be
differential access to social information based on children's postural
developments: crawling infants would see fewer faces because they would
primarily be looking at the ground, and walking toddlers would have
access to a richer visual landscape that would contain a larger portion
of the social information in the environment.

@@

We used three face detection systems to explore infants' changing access
to social information and to avoid the cost of hand-annotating every
frame. The first of these is the most commonly-used and widely available
face detection algorithm: Viola-Jones. We used this as a benchmark for
performance, and while it can achieve impressive accuracy in some
situations, it is notoriously bad at dealing with occluded faces
(Scheirer, Anthony, Nakayama, \& Cox, 2014). We next capitalized on
recent improvements in computer vision, testing the performance of two
face detectors that both made use of Convolutional Neural Networks
(CNNs) to extract face information. The first algorithm was specifically
optimized for face detection, and the second algorithm was optimized to
extract information about the position of 18 different body parts
belonging to an agent.

This second of the CNN-based algorithms--the pose detector--provided us
(along with other parts) with the location of an agent's wrists, which
we used as a good proxy for the presence of a hand. We did so first
because we did not capture the entire visual field experienced by the
infants/children. Thus, even though the video may only show the presence
of a wrist, the caregiver's hand may be within the child's field of
view. Second, we did so because hands are often occluded by objects when
caregivers are interacting with children, yet still visually accessible
by the child and part of their joint interaction. For example, if a
caregiver was holding a toy and presenting it to the infant, their
wrists may be visible but their hand may not necessarily be (as it is
occluded by the toy). Similarly, we used the nose (one of the 18 body
parts detected) to operationalize face presence, as any half of a face
necessarily contains a nose.

@@

To evaluate face detector performance, we needed to construct an
unbiased ``gold set'' of labeled frames that made sure to account for
the relatively rare appearance of faces in the dataset. We thus
hand-labeled two samples: a sample containing a high density of faces
(half reported by MTCNN, half by OpenPose) and a random sample from the
remaining frames. Each sample was comprised of an equal number of frames
taken from each participant (i.e., video). Faces were classifed as
present in a frame if at least half of the face was showing. Precision
(hits / hits + false alarms), recall (hits / hits + misses), and F-score
(harmonic mean of precision and recall) were calculated for all
detectors and are reported in Table 2. For wrist detections, the ``gold
set'' was constructed in the same manner, with the exception that frames
with a high density of wrists were taken by wrist detections made by
OpenPose.

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose); thus the face
presence analyses to follow all result from MTCNN detections. We found
that although MTCNN and OpenPose perform comparably with the random
sample, MTCNN performed better on the high density sample (specifically
looking at precision), suggesting that OpenPose generated more false
positives than MTCNN. ViolaJones performed quite poorly relative to the
other detectors especially on the random sample.

@@

We noted characteristic changes in infants' posture and orientation
across this developmental time range. The proportion of time infants
spent sitting decreased with age, and the proportion of time infants
spent standing increased with age. Both 8-month-olds and 12-month-olds
spent equivalent amounts of time either lying/crawling, which was
markedly decreased in the 16-month-olds, who spent most of their time
either sitting or standing (see Figure \ref{fig:posture}). We also
observed characteristic changes in children's orientation relative to
their caregivers: the 8-month-olds spent more time with their caregiver
behind them supporting their sitting positions (see Figure
\ref{fig:posture}).

>>>>

However, as children are learning from others around them, their view of
the world is also changing radically (K. Adolph \& Berger, 2007).
Infants' motor abilities improve dramatically near the end of the first
year of life, allowing them to locomote independently. These motor
changes have drastic consequences for what children see; crawling and
walking infants have radically different views of the world. For
example, during spontaneous play in a laboratory playroom, toddlers are
more likely to look at the floor while crawling than while walking (J.
Franchak, Kretch, Soska, \& Adolph, 2011); in general, walking infants
tend to have full visual access to their environment and the people in
it, while crawling infants do not (K. S. Kretch, Franchak, \& Adolph,
2014).

@@

Here, we directly ask whether postural and locomotive developments
change the availability of social information--the presence of faces and
hands. To do so, we recorded the visual experience of a group of infants
in three age ranges (8,12, and 16 months) using head-mounted cameras
during a brief laboratory free-play session; children's posture and
orientation relative to their caregiver were also recorded from a
third-person perspective and hand-annotated. We then capitalize on
recent improvements in face and pose detection algorithms (Cao, Simon,
Wei, \& Sheikh, 2017; K. Zhang, Zhang, Li, \& Qiao, 2016) to analyze the
frequencies of faces and hands (using wrists as a proxy for the latter)
in the child's visual environment, both overall and relative to naming
events by their caregivers. We hypothesized that there would be
differential access to social information based on children's postural
developments: crawling infants would see fewer faces because they would
primarily be looking at the ground, while walking toddlers would have
access to a richer visual landscape thus enabling a larger portion of
the social information in their environment to be accessible.

that would contain a larger portion of the social information in the
environment.

@@

We used three face detection systems to explore infants' changing access
to social information and to avoid the cost of hand-annotating every
frame. The first of these is the most commonly-used and widely available
face detection algorithm: Viola-Jones. We used this as a benchmark for
performance; while it can achieve impressive accuracy in some
situations, it is notoriously bad at dealing with occluded faces
(Scheirer, Anthony, Nakayama, \& Cox, 2014). We next capitalized on
recent improvements in computer vision, testing the performance of two
face detectors that both made use of Convolutional Neural Networks
(CNNs) to extract face information. The first algorithm was specifically
optimized for face detection, and the second algorithm was optimized to
extract information about the position of 18 different body parts
belonging to an agent.

This second of the CNN-based algorithms--the pose detector--provided us
with the location of an agent's wrists, which we used as a proxy for the
presence of a hand. We did so first because we did not capture the
entire visual field experienced by the infants/children. Thus, even
though the video may only show the presence of a wrist, the caregiver's
hand may be within the child's field of view. Second, we did so because
hands are often occluded by objects when caregivers are interacting with
children, yet still visually accessible by the child and part of their
joint interaction. For example, if a caregiver was holding a toy and
presenting it to the infant, their wrists may be visible but their hand
may not necessarily be (as it is occluded by the toy). Similarly, we
used an agent's nose (one of the 18 body parts detected) to
operationalize face presence, as any half of a face necessarily contains
a nose.

@@

To evaluate face detector performance, we needed to construct an
unbiased ``gold set'' of labeled frames that made sure to account for
the relatively rare appearance of faces in the dataset. We thus
hand-labeled two samples: a sample containing a high density of faces
(half reported by MTCNN, half by OpenPose) and a random sample from the
remaining frames. Each sample was comprised of an equal number of frames
taken from each participant (i.e., video). Faces were classifed as
present in a frame if at least half of the face was showing. Precision
(hits / hits + false alarms), recall (hits / hits + misses), and F-score
(harmonic mean of precision and recall) were calculated for all
detectors and are reported in Table 2. For wrist detections, the ``gold
set'' was constructed in the same manner, with the exception that frames
with a high density of wrists were taken by pose detections made by
OpenPose.

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose); thus the face
presence analyses to follow all result from MTCNN detections. We found
that although MTCNN and OpenPose perform comparably with the random
sample, MTCNN performed better on the high density sample (specifically
looking at precision), suggesting that OpenPose generated more false
positives than MTCNN. ViolaJones performed quite poorly relative to the
other detectors especially with respect to the random sample.

@@

We noted characteristic changes in infants' posture and orientation
across this developmental time range. The proportion of time infants
spent sitting decreased with age, and the proportion of time infants
spent standing increased with age. Both 8 month-olds and 12 month-olds
spent equivalent amounts of time either lying/crawling, which was
markedly decreased in the 16-month-olds, who spent most of their time
either sitting or standing (see Figure \ref{fig:posture}). We also
observed characteristic changes in children's orientation relative to
their caregivers: the 8-month-olds spent more time with their caregiver
behind them supporting their sitting positions (see Figure
\ref{fig:posture}).
